### 2020-02-01 Common/chapters/paper_reproduction.tex
Johan and Julien: gradient flow section first draft

\chapter{Paper reproduction}
\label{ch:paper_reproduction}
This chapter relies on the article "Computer-Aided Diagnosis of Prostate Cancer Using a Deep Convolutional Neural Network from Multiparametric MRI" from Song et al.\cite{07}, shortly presented in chapter \ref{ch:literature_review}. It aims at reproducing the experiment of the paper in order to acquire the medical, theoretical and technical background before proposing a transfer learning method as a way to improve the classification using other body parts, which overcome the lack of available data (see chapter \ref{ch:transfer_learning}).\\
Song et al. \cite{07} proposed a deep convolutional neural network (DCNN) method to detect prostate cancer based on the SPIE-AAPM-NCI PROSTATEx Challenge dataset. This dataset is one of the biggest available dataset for prostate cancer classification. The two different output classes of the latter are benign lesion (class 0) and malignant lesion (class 1). This paper explains all the steps to follow with the goal of building a computer-aided-diagnosis (CAD) system for prostate cancer detection. Moreover, it also provides results about the algorithm performance, which can be used as a benchmark to compare with the results of the reproduction of the experiment. However, since the article gives no information about the results their model got on the official PROSTATEx challenge test set, the reproduction of the experiment will fill that gap.\\
This chapter is built top-down: first a superficial overview of the entire process is established in order to understand the purpose of the experiment as a whole. Then, each part or theoretical notion of the experiment is deeply described. The structure of the dataset is detailed, all steps of its processing are explained and the techniques used as verification of the proper functioning of the algorithm are presented. After the processing of the data, the training phase is deepened and all hyperparameters, options and implementation choices are given to ensure the reproductibility of the experiment. This part is followed by the presentation of the raw results, which is itself followed by their analysis in the "discussion" section.

@@

@@

\subsection{Training verification}
\subsubsection{Gradient flow visualization}

\section{Results}

>>>>

\chapter{Paper reproduction}
\label{ch:paper_reproduction}
This chapter relies on the article "Computer-Aided Diagnosis of Prostate Cancer Using a Deep Convolutional Neural Network from Multiparametric MRI" from Song et al.\cite{07}, shortly presented in chapter \ref{ch:literature_review}. It aims at reproducing the experiment of the paper in order to acquire the medical, theoretical and technical background before proposing a transfer learning method as a way to improve the classification using other body parts, which overcome the lack of available data in the medical field (see chapter \ref{ch:transfer_learning}).\\
Song et al. \cite{07} proposed a deep convolutional neural network (DCNN) method to detect prostate cancer based on the SPIE-AAPM-NCI PROSTATEx Challenge dataset. This dataset is one of the biggest available dataset for prostate cancer classification. The two different output classes of the latter are benign lesion (class 0) and malignant lesion (class 1). This paper explains all the steps to follow with the goal of building a computer-aided-diagnosis (CAD) system for prostate cancer detection. Moreover, it also provides results about the algorithm performance, which can be used as a benchmark to compare with the results of the reproduction of the experiment. However, since the article gives no information about the results their model got on the official PROSTATEx challenge test set, the reproduction of the experiment will fill that gap.\\
This chapter is built top-down: first a superficial overview of the entire process is established in order to understand the purpose of the experiment as a whole. Then, each part or theoretical notion of the experiment is deeply described. The structure of the dataset is detailed, all steps of its processing are explained and the techniques used as verification of the proper functioning of the algorithm are presented. After the processing of the data, the training phase is deepened and all hyperparameters, options and implementation choices are given to ensure the reproductibility of the experiment. This part is followed by the presentation of the raw results, which is itself followed by their analysis in the "discussion" section.

@@

\caption{Complete list of script options}
\label{fig:paper_reproduction_options}

@@

\subsection{Training verification}
In deep learning, two main problems can occur during training. The first one is called the "vanishing gradient" problem and refers to the fact that it is possible for the loss function to compute extremely small gradients, near zero. Consequently, the weight update is also extremely small, which makes the neural network hard or impossible to train. The second problem, the "exploding gradient" is the opposite. Concretely, in this case, large gradients are computed, which results in huge weight updates that can even reach "NaN" values. This makes the model unstable and unable to learn from training data.  \\
As a result, it is important to analyse the gradient propagation across the network to ensure not been face to such problems. To achieve this goal, a visualization of all gradients of the network is implemented. This allows to visually notice the gradient flow at a glance and to see its evolution during all epochs (one visualization per batch is generated).
\subsubsection{Gradient flow visualization}
The visualization displays the gradient flow through the entire neural network. It shows the name of each layer on the x-axis and its average gradient value on the y-axis (recall: for each layer the gradient is a matrix). Furthermore, it also gives information about the max value of the gradient and indicates in black if one of them is equal to zero.\\
The figure \ref{fig:gradient_flow} shows the gradient flow at epoch 0, batch 6. From the output layer (called "last\_layer0.weight" on the graph) to the first layer the gradient is well propagated: no huge average gradients are registered, neither extremely small ones.

\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/gradient_flow.png}
\caption{Gradient flow at epoch 0, batch 6 of the experiment}
\label{fig:gradient_flow}
\end{figure}
\section{Results}
